---
title: "IATTC Public Domain Data"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme:
      bootswatch: united
    logo: logo.png
    favicon: logo.png
resource_files:
- iattc_pd.sqlite3
---

# Historical by Spp. {data-orientation=rows}

```{r setup, include=FALSE, context = "server"}
library(flexdashboard)
library(shiny)
library(dygraphs)

#Install once using
#devtools::install_github("dawidh15/skillsTools", auth_token = "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",upgrade = "never")
# THen comment out

library(skillsTools)
# library(leaflet)
# bslib::bs_themer() # Activates Theme selection tool
# thematic::thematic_rmd() # set ggplot in theme colors

# ------------CACHE----------------
# Store cache on disk, is persistent across R processes
# Otherwise, cache is stored in memory
# See https://shiny.rstudio.com/articles/caching.html
#shinyOptions(cache = cachem::cache_disk(file.path(dirname(tempdir()), "myapp-cache")))
shinyOptions(cache = cachem::cache_disk(path_join(c(".","appCache"))))

dat_sp_catch_by_spp <- GetTable(".", "General Spatial Data")
dat_spp_time <- GetTable(".", "Catch Time Series By Species")
dat_prop_ctch <- GetTable(table_name = "Proportional Catches by Period-Flag")
dat_flag_time <- GetTable(table_name = "Catch Time Series By Flag")
dat_sp_flag_period <- GetTable(table_name = "Catch By Space-Period-Flag")

```

## Column {.sidebar data-width=200}

```{r}
selectInput("selectedSpp"
            , label = "Select a species"
            , choices = skillsTools::GetSppNames(".")
            , multiple = FALSE
            , selected = "ALL")

actionButton("submitP1", label = "Apply", icon = icon("filter"))
```


## Map Page 1  {data-height=300}

### Instructions

- First Page contains of catches by species.
    - Select a species in the dropdown list
    - Click apply generate the plots.
    - Note that images are cached (image are shown quicker for previously selected data)
- Second tab shows general information of catches by country (flag)
    - Use the play button to watch an animation.
- Third tab shows detailed information about species caught by flag.
    - Click "Apply Filter" to see the changes.

### Historical catches by species

```{r}
# Get spp from input when Apply button is pressed
# add ignoreNULL = FALSE, this allows to use the default selected value for the input
#this_spp <- eventReactive(input$submitP1, valueExpr = input$selectedSpp,ignoreNULL = FALSE)

```


```{r}
fillCol(
  plotOutput( "HistoricalCatchMap", height = "100%" )
)
output$HistoricalCatchMap <- 
  renderPlot( MapCatchesBySpp(filter(dat_sp_catch_by_spp, Species == input$selectedSpp ))) %>% 
  bindCache(input$selectedSpp) %>% 
  bindEvent(input$submitP1, ignoreNULL = FALSE)
```

## Time series by spp {data-height=150}
### Historical catch (mt)

```{r}
fillCol(
 dygraphOutput("CatchTimeSeries", height = "100%") 
)

output$CatchTimeSeries <- 
  renderDygraph({
    # browser()
    plot_dat_spp_time <-
      dat_spp_time %>%
      filter(Species == input$selectedSpp) %>%
      select(-Species)
    dygraph(plot_dat_spp_time) %>% 
      dyRangeSelector() }) %>% 
  bindCache(input$selectedSpp) %>% 
  bindEvent(input$submitP1, ignoreNULL = FALSE)
```


# Flag {data-orientation=rows}

## Input {.sidebar data-width=200}

```{r}
defaultFlag <- pull(skillsTools::GetFlagNames("."), Flag) %>% first()

selectInput("selectedFlagGeneral"
            , label = "Select a Flag"
            , choices = skillsTools::GetFlagNames(".")
            , multiple = FALSE
            ,selected = defaultFlag)
periods <- skillsTools::GetTimePeriod(".")


sliderInput(
  "sliderPeriodFlag",
  "Select a time period",
  value = max(periods),
  min = min(periods),
  max = max(periods),
  step = 1L,
  animate = animationOptions(interval = 3000, loop = TRUE)
)

minyear <- 
  reactive(
    {
      dat_sp_flag_period %>% 
        filter(Flag == input$selectedFlagGeneral & Period == input$sliderPeriodFlag) %>% 
        pull(MinYear) %>% 
        min()
    }
  ) %>% 
  bindCache(input$selectedFlagGeneral, input$sliderPeriodFlag)

maxyear <- 
  reactive(
    {
      dat_sp_flag_period %>% 
        filter(Flag == input$selectedFlagGeneral & Period == input$sliderPeriodFlag) %>% 
        pull(MaxYear) %>% 
        max()
    }
  ) %>% 
  bindCache(input$selectedFlagGeneral, input$sliderPeriodFlag)
```


## Header {data-height = 100}

### Flag and period

```{r}
output$headerFlagPeriod <- 
  renderValueBox( {
    my <- ifelse(is.finite(minyear()), minyear(), "No-Data")
    mxy <- ifelse(is.finite(maxyear()), maxyear(), "No-Data")
    flexdashboard::valueBox(
      glue("Flag: {input$selectedFlagGeneral}. Period from:  {my} to {mxy}.")
    ,caption = "Historical catches by flag", color = "blue")
  }
  )
    
    
valueBoxOutput("headerFlagPeriod")
```

## Fleet expansion {data-height 300}

### Catches by flag (mt) {data-width=150}

```{r}
plotOutput( "FlagCatchMap", height = "100%" )

output$FlagCatchMap <- 
  renderPlot( 
    {
      filtered_dat_sp_flag_period <- filter(dat_sp_flag_period,
                 Flag == input$selectedFlagGeneral & Period == input$sliderPeriodFlag)
      
      if (nrow(filtered_dat_sp_flag_period) == 0)
      {
        filtered_dat_sp_flag_period <- data.frame()
      } 
          MapCatchesBySpp( filtered_dat_sp_flag_period )
    } # End render Plot
 )  %>% 
  bindCache(input$selectedFlagGeneral, input$sliderPeriodFlag)

```


### Historical catches by flag (mt) {data-width=300}

```{r}
fillCol(
 dygraphOutput("CatchTimeSeriesFlag", height = "100%") 
)

output$CatchTimeSeriesFlag <- 
  renderDygraph({
    # browser()
    plot_dat_flag_time <-
      dat_flag_time %>%
      filter(Flag == input$selectedFlagGeneral) %>%
      select(-Flag)
    dygraph(plot_dat_flag_time) %>% dyRangeSelector()
  }) %>% 
  bindCache(input$selectedFlagGeneral) 
```


# Flag Detailed {data-orientation=rows}

## Input {.sidebar data-width=200}

```{r}
defaultFlag <- pull(skillsTools::GetFlagNames("."), Flag) %>% first()

selectInput("selectedFlag"
            , label = "Select a Flag"
            , choices = skillsTools::GetFlagNames(".")
            , multiple = FALSE
            ,selected = defaultFlag)
periods <- skillsTools::GetTimePeriod(".")


sliderInput(
  "sliderPeriod",
  "Select a time period",
  value = max(periods),
  min = min(periods),
  max = max(periods),
  step = 1L
)
 
actionButton("submitP2", label = "Apply", icon = icon("filter"))
```


```{r}
ScaledCatchesData <- 
  reactive({
    dat_prop_ctch %>% 
      filter(Period == input$sliderPeriod & Flag == input$selectedFlag)
  }) %>% 
  bindEvent(input$submitP2, ignoreNULL = FALSE)

ranks <- reactive({ 
  dat_prop_ctch %>% 
    filter(Period == input$sliderPeriod) %>%
    pull(Ranking) %>%
    max(na.rm = TRUE)
  }) %>% 
  bindEvent(input$submitP2, ignoreNULL = FALSE)

thisRanking <- reactive({ 
  dat_prop_ctch %>% 
    filter(Period == input$sliderPeriod & Flag == input$selectedFlag) %>%
    pull(Ranking) %>%
    min(na.rm = TRUE)
  }) %>% 
  bindEvent(input$submitP2, ignoreNULL = FALSE)

maxCatch <- 
  reactive({ 
  dat_prop_ctch %>% 
    filter(Period == input$sliderPeriod) %>%
    pull(Weight) %>%
    max(na.rm = TRUE) %>%
    formatC(big.mark = " ",format = "f", digits = 0)
  })  %>% 
  bindEvent(input$submitP2, ignoreNULL = FALSE)

```


## Row


### Maximum Catch of a species by period

```{r}
    valueBoxOutput("MaximumCatch")

output$MaximumCatch <- renderValueBox(
  valueBox(maxCatch(), caption = "Max Catch by species (mt), during this period")
)
```


### Relative fishing pressure

```{r}
gaugeOutput("FlagRank")


output$FlagRank <-
  renderGauge(
    gauge(
    round(100 * (ranks() / thisRanking()) / ranks(), digits = 0),
    min = 0,
    max = 100,
    #symbol ='%',
    sectors = gaugeSectors(
      success = c(0,25),
      warning = c(26,75),
      danger = c(76,100),
      colors = c("blue", "yellow", "red")
    )
    , label = "Fishing Pressure"
  )
)
```

## Scaled Catches (% of max catch)

```{r}

fillCol(plotOutput("ScaledCatches"))
output$ScaledCatches <- 
  renderPlot(PlotByFlag(ScaledCatchesData()))
```

